---
title: "Q7_EGARCH"
author: "Kamin Atsavasirilert"
date: "2024-09-24"
output: html_document
---

```{r setup, include=FALSE}
library(fGarch)
library(rugarch)
```


# Read and prepare data
```{r cars}
data = read.csv("m-gmsp5008.txt", sep="")
log_ret = log(data$gm + 1)
```
## Q7.a As omega term is not statistically different from 0 with 95% confidence level, we should remove it from the model.
```{r pressure, echo=FALSE}
model = garchFit(~garch(1,1), data=log_ret, trace=FALSE, cond.dist = "norm")
summary(model)
```
## Q7.b As the estimated shape v = 9.418 with S.E. = 2.968, the t-statistic of v = (9.418-6)/2.968 = 1.15, meaning we do not have enough evidence to reject the null hypothesis.
```{r 1, echo=FALSE}
t_model = garchFit(~garch(1,1), cond.dist = "std", data=log_ret, trace=FALSE)
summary(t_model)
```
## Q7.c As the fitted model indicates no significance for omega term, we should exclude it and the rest parameters should work fine.
```{r 2, echo=FALSE}
tmp_egarch = ugarchspec(variance.model=list(model="eGARCH", garchOrder=c(1,1)),
                          mean.model=list(armaOrder=c(0,0), include.mean=TRUE),
                          distribution.model="norm")
egarch_model = ugarchfit(data = log_ret, spec = tmp_egarch)
egarch_model
```